The Expected Place of the Local Group in the Cosmic Web

### 2014-08-12 paper/main.tex
overdensity, ellipticity and and prolateness

We now describe the preferred place of the LG samples in terms of the
web overdensity, ellipticiy and anisotropy as defined in Section
\ref{sec:simulation}.

Figure \ref{fig:median_overdensity} shows dependency of the web overdensity,
ellipciticy, and prolateness on pair mass for the different samples.
GS is represented by the solid lines with the associated 
errors covered by the shaded region. 
The symbols represents the results for the $2\sigma$ and $3\sigma$
samples.  
In all cases it is immediatly clear that the range of values for the
$2\sigma$ and $3\sigma$ samples are completely expected from its mass
dependence.

Left panel shows the overdensity dependence on pair mass. 
Higher mass pairs are located in high density regions.
The $2\sigma$ and $3\sigma$ samples having a narrower mass range as 
shown in previous figure, are consequently located within a narrower 
range of overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1$. 
This is also consistent with the fact that these samples are mostly 
found in filaments and sheets. 
The average overdensity of $2\sigma$ and $3\sigma$ samples is expected
from the values in the GS within the same mass range.

Middle and right panels show web ellipciticy and absolute prolateness
dependence on mass. Again we noticed that within the same mass range,
the $2\sigma$ and $3\sigma$ average ellipciticy and prolateness does not
differ significantly from GS
For the $2\sigma$ and $3\sigma$ samples most of the pairs are located
in a narrow range for ellipticities in the range $0.1<e<1.0$, and
prolateness $|p|<0.5$.

>>>>

We now characterize the preferred place of the LG samples in terms of the
web overdensity, ellipticiy and anisotropy as defined in Section
\ref{sec:simulation}.

Figure \ref{fig:median_overdensity} shows the dependency of these three
characteristics  on the total pair mass for the different samples.
GS is represented by the solid lines with the associated 
errors covered by the shaded region. 
The symbols represents the results for the $2\sigma$ and $3\sigma$
samples.   
In thre three cases it is evident that the range of values for the
$2\sigma$ and $3\sigma$ samples are completely expected from the mass
constraint alone.

The left panel shows the overdensity dependence on pair mass. 
Higher mass pairs are located in high density regions.
The $2\sigma$ and $3\sigma$ samples having a narrower mass range as 
shown in previous figure, are consequently located within a narrower 
range of overdensities $0.0<\delta<2.0$ peaking at $\delta \sim 1$. 
This is also consistent with the fact that these samples are mostly 
found in filaments and sheets.

Middle and right panels show web ellipciticy and absolute prolateness
dependence on mass. 
Again we notice that within the $2\sigma$ and $3\sigma$ mass range,
the average ellipciticy and prolateness does not differ significantly
from the GS expectation.
In the RS samples the pairs are located in a narrow range for
ellipticities $0.1<e<1.0$ and absolute prolateness $|p|<0.4$.
